---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rugger  

:new_zealand: :ireland: `r emo::ji("wales")` `r emo::ji("england")` :south_africa: :australia: `r emo::ji("scotland")` :fiji: ^[Black flags?! They're Github's fault. The flags represent the rankings as of the end of 2018 -- New Zealand, Ireland, Wales, England, South Africa, Australia, Scotland and Fiji. You can see them in R with `emo::ji("wales")`, for example, using the emo package, available from [https://github.com/hadley/emo](https://github.com/hadley/emo).]

rugger is a rrrrugby package :rugby_football:. Get stats on teams, players, rankings and calculate changes in the rankings for a certain match. 

## Installation

You can install rugger with:

``` {r eval = FALSE}
remotes::install_github("RobertMyles/rugger")
```

I won't be burdening CRAN with it.  

## Usage

You can see the current world rankings with `get_rankings()`:

```{r}
library(rugger)
get_rankings()
```

Hmmm, what would happen if New Zealand played Ireland tomorrow, and Ireland won by 5 points?
```{r}
calculate_rank("New Zealand", "Ireland", score = c(15, 20))
```

Let's have a look at the history between England and Scotland, the first two teams to play the game:
```{r}
get_team_records("England", "Scotland")
```

England winning almost 62% of the matches there. 

I wonder which player has scored most tries in rugby?

```{r message=FALSE, warning=FALSE}
library(dplyr)

get_team_records(type = "player") %>% 
  arrange(desc(points)) %>% 
  select(player, points)
```

The sublime Dan Carter!

## Data etc.

All of the data acessed by this package is obviously for informational/educational use, and a big thanks to all for making it available. 

It belongs to [World Rugby](https://www.world.rugby/rankings/mru) and [ESPN](http://stats.espnscrum.com/statsguru/rugby/stats/index.html). The algorithm that calculates the rankings also belongs to World Rugby, you can read about it [here](https://www.world.rugby/rankings/explanation). 
Some of the data is also pulled from [Pick and Go](http://www.lassen.co.nz/pickandgo.php) by [Lassen Creative Technologies](http://www.datacleanse.co.nz/).  
